Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array

### 2016-03-06 ForegroundSimulations/ms.tex
Correct typos
From 3f81d66 (fgsim):
====================

In ms.tex,

(*) Correct typos

For reference, we use two models of EoR. In the first, simulations of the H{\sc i} signal were created using the publically available 21cmFAST\footnote{\url{http://homepage.sns.it/mesinger/DexM\_\_\_21cmFAST.html}} code described in \citet{mes11}. The code uses the excursion set formalism of \citet{fur04a} to generate ionization and 21cm brightness fields for numerous redshifts. The model shown in this paper assumes the same fiducial values as in \citet{ewa16}: $T_\text{vir}^\text{min} = 2 \times 10^4$~K (virial temperature of minimum mass of dark matter halos that host ionizing sources), $\zeta = 20$ (ionization efficiency), and $R_\text{mfp}=15$~Mpc (mean free path of UV photons) which predicts the redshift of 50\% ionization (and hence a peak in the power spectrum signal) to be at $z=8.5$. The second EoR model is borrowed from the simulations described in detail in \citet{lid08}. Hereafter, we refer to these two as EoR models 1 and 2 respectively.

>>>>

For reference, we use two models of EoR. In the first, simulations of the H{\sc i} signal were created using the publicly available 21cmFAST\footnote{\url{http://homepage.sns.it/mesinger/DexM\_\_\_21cmFAST.html}} code described in \citet{mes11}. The code uses the excursion set formalism of \citet{fur04a} to generate ionization and 21cm brightness fields for numerous redshifts. The model shown in this paper assumes the same fiducial values as in \citet{ewa16}: $T_\text{vir}^\text{min} = 2 \times 10^4$~K (virial temperature of minimum mass of dark matter halos that host ionizing sources), $\zeta = 20$ (ionization efficiency), and $R_\text{mfp}=15$~Mpc (mean free path of UV photons) which predicts the redshift of 50\% ionization (and hence a peak in the power spectrum signal) to be at $z=8.5$. The second EoR model is borrowed from the simulations described in detail in \citet{lid08}. Hereafter, we refer to these two as EoR models 1 and 2 respectively.
